Binary companions of red giant stars in \apogee\ \DR

### 2018-02-28 paper/1-catalog/twoface-catalog.tex
details about the control sample run

We also run on the null control sample (see \sectionname~\ref{sec:control}) with
the same parameters.
\todo{summary of this run - do any stars get flagged as needs MCMC/etc?}

>>>>

We also run on the null control sample (see \sectionname~\ref{sec:control}) with
the same parameters.
From the control sample run, 13 ``stars'' are flagged as \emph{needs MCMC}, and
1023 are flagged as ``needs more prior samples'';
For these stars, we don't continue sampling with \thejoker\ or MCMC and only use
the posterior samples returned from the \thejoker.
% See: Sample K cuts.ipynb
